### 2022-11-04 pv_evaluation/templates/inventor/callouts/entropy-tips.qmd
version 1.0.0 draft

For $q=2$, the Hill number is the probability that two randomly sampled inventors have the same number of authored patents:
$$
    H_2 = \sum_{i=1}^{\infty} p_i^2.
$$

>>>>

For $q=2$, the Hill number is the inverse of the probability that two randomly sampled inventors have the same number of authored patents:
$$
    H_2 = \sum_{i=1}^{\infty} p_i^2.
$$
